Advancing Sustainable Mobility: A GIS-Based Multi-Criteria Decision Analysis for Equitable Electric Vehicle Supply Equipment Deployment in Philadelphia

### 2025-02-19 code/MCDA-EVSE.Rmd
Update MCDA-EVSE.Rmd

@@

model1 <- lm(topsis_percentile_c1 ~ topsis_percentile, data = TOPSIS_c1_cp)
model2<- lm(topsis_percentile_c1 ~ topsis_percentile_c1_org, data = TOPSIS_c1_cp)
model3 <- lm(topsis_percentile ~ topsis_percentile_c1_org, data = TOPSIS_c1_cp)

@@

```{r fig.height=14, fig.width=14}

>>>>

```{r global and local score combined }

global_local <- TOPSIS %>% 
  mutate(global_val = values) %>% 
  mutate(global_rank = topsis_rank) %>% 
  left_join(TOPSIS_c1 %>% mutate(c1_val = values) %>% dplyr::select(uniqueID, c1_val), by = "uniqueID") %>%
  left_join(TOPSIS_c2 %>% mutate(c2_val = values) %>% dplyr::select(uniqueID, c2_val), by = "uniqueID") %>%
  left_join(TOPSIS_c3 %>% mutate(c3_val = values) %>% dplyr::select(uniqueID, c3_val), by = "uniqueID") %>%
  left_join(TOPSIS_c4 %>% mutate(c4_val = values) %>% dplyr::select(uniqueID, c4_val), by = "uniqueID") %>%
  mutate(local_val = coalesce(c1_val, c2_val, c3_val, c4_val)) %>%
  mutate(local_rank = min_rank(desc(local_val))) %>%
  dplyr::select(uniqueID, global_val, global_rank, local_val, local_rank)

global_local_toplot <- fishnet_nowater %>% 
  dplyr::select(uniqueID, geometry) %>%
  left_join(global_local, by = "uniqueID")

quantiles_glo <- classIntervals(global_local_toplot$global_val, n = 6, style = "quantile")
quantiles_loc <- classIntervals(global_local_toplot$local_val, n = 6, style = "quantile")

global_local_toplot$quantile_glo <- cut(global_local_toplot$global_val, breaks = quantiles_glo$brks, include.lowest = TRUE)
global_local_toplot$quantile_loc <- cut(global_local_toplot$local_val, breaks = quantiles_loc$brks, include.lowest = TRUE)

ggplot()+
  geom_sf(data=fishnet, color="black", fill="white") +
 geom_sf(data = global_local_toplot, aes(fill = quantile_loc), color = "black") +
  scale_fill_brewer(palette = "Blues") + 
  labs(title = "Local TOPSIS Score", fill = "Bins") +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks =element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.subtitle = element_text(size = 9,face = "italic"),
        plot.title = element_text(size = 12, face = "bold"),
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill=NA, size=0.8)
        )

@@

model1 <- lm(topsis_percentile_c1 ~ topsis_percentile, data = TOPSIS_c1_cp)
model2<- lm(topsis_percentile_c1 ~ topsis_percentile_c1_org, data = TOPSIS_c1_cp)
model3 <- lm(topsis_percentile_c1_org ~ topsis_percentile, data = TOPSIS_c1_cp)

@@

```{r sankey, fig.height=14, fig.width=14}
